\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Harshil Patel} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+91 7887710001 \\ Bhavnagar, India} 
\address{\href{mailto:pharshil748@gmail.com}{pharshil748@gmail.com} \\ \href{https://www.linkedin.com/in/harshil748/}{Linkedin} \\ \href{https://harshilpatel.me}{harshilpatel.me}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Computer engineering student with knowledge in programming, machine learning, and cybersecurity.
Currently seeking a summer internship to apply and grow my skills in a collaborative and innovative environment.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Bachelor of Technology Computer Engineering}, CHARUSAT University \hfill {Expected 2027}

{\bf Minor in Artificial Intelligence}, IIT Mandi   \hfill  {Expected 2026}
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills & Python, Java, JavaScript, React, Node.js, SQL, MongoDB, Tailwind CSS
\\
Soft Skills & Problem Solving, Communication, Self-Learning, Time Management\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{FrontEnd Intern} \hfill May 2025 - June 2025\\
Meetanshi Technologies LLP \hfill \textit{Bhavnagar, IN}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Improved 30\% UI responsiveness of the TimeTrackr web application by optimizing React components and Tailwind CSS layouts with React.js, Tailwind CSS, and performance debugging tools.
     \item Directed the full redesign and execution of the task management module, increasing user engagement by 25\% and improving user workflows for admins and team members.
    \item Designed and implemented a reusable and modular frontend component library for analytics, timers, and tasks based on React.js, Tailwind CSS, and Recharts to support fast feature development with uniform design patterns. 
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{TimeTrackr.} {Built a full-stack web app using React, Node.js, MongoDB, Recharts, and JWT/Google OAuth for secure login. Tracked user work sessions and productivity trends in real-time, reducing manual timesheet entries by 40\% during internship deployment at Meetanshi.}
\item \textbf{PyLock.} {Developed a desktop password manager using Python, Tkinter, SQLite, smtplib, and Cryptography, supporting AES encryption, 2FA via email, and recovery via secret phrase. Successfully improved credential safety and recovery flow for local users in penetration test lab setup.}
\item \textbf{Short Project Title.} {Build a project that does something and had quantified success using A, B, and C. This project's description spans two lines and also won an award.}
\item \textbf{Line Following Car.} {Built an Arduino-based car using IR sensors, L298N motor driver, and C++ logic to autonomously follow black-and-white lines. Demonstrated real-time turning and track correction; showcased in embedded systems project expo.}
\item \textbf{TraceTrackers – Smart India Hackathon 2024.} {Designed a blockchain analysis tool to trace crypto transactions linked to drug trafficking using Neural Networks and blockchain analytics. Detected suspicious transaction patterns with high accuracy. Selected for the SIH 2024 software edition finals, representing the institute.}
\end{rSection} 

\end{document}